---
title: "E-Vehicle Incentive Impact Tool Report"
date: "`r format(Sys.Date(), '%m-%d-%y')`"
output: html_document

params: 
  Car_Trip_Avg_Length: Car_Trip_Avg_Length
  EBike_per_budget: EBike_per_budget
  test_budget: test_budget
  PHEV_incentive: PHEV_incentive
  BEV_econ: BEV_econ
  FCEV_incentive: FCEV_incentive
  preset_FCEV: preset_FCEV
  FCEV_include: FCEV_include
  preset_EBike: preset_EBike
  EBike_include: EBike_include
  BEV_incentive: BEV_incentive
  EBike_econ: EBike_econ
  EBike_Battery_Storage: EBike_Battery_Storage
  EBike_incentive: EBike_incentive
  BEV_per_budget: BEV_per_budget
  EBike_VMT_r: EBike_VMT_r
  preset_Car_Trips_Daily_Avg: preset_Car_Trips_Daily_Avg
  FCEV_econ: FCEV_econ
  PHEV_elec_econ: PHEV_elec_econ
  PHEV_range_elec: PHEV_range_elec
  preset_PHEV: preset_PHEV
  BEV_include: BEV_include
  elec_gen_emissions: elec_gen_emissions
  preset_elec_gen_emissions: preset_elec_gen_emissions
  PHEV_per_budget: PHEV_per_budget
  preset_BEV: preset_BEV
  FCEV_per_budget: FCEV_per_budget
  ICE_Fuel_Economy: ICE_Fuel_Economy
  Car_Trips_Daily_Avg: Car_Trips_Daily_Avg
  PHEV_ICE_econ: PHEV_ICE_econ
  renew_energy_ratio: renew_energy_ratio
  PHEV_include: PHEV_include
  preset_ICE_Fuel_Economy: preset_ICE_Fuel_Economy
  costperkg: costperkg
  costperkg_x: costperkg_x
  costperkg_y: costperkg_y
  test_points: test_points
  num_incentivized: num_incentivized
  test_budget_points: test_budget_points
  num_x: num_x
  num_y: num_y
  CO2_saved: CO2_saved
  test_budget_points_w_CO2: test_budget_points_w_CO2
  CO2_saved_x: CO2_saved_x
  CO2_saved_y: CO2_saved_y
  num_incentivized_distrib: num_incentivized_distrib
  test_budget_points_distrib: test_budget_points_distrib
  CO2_saved_distrib: CO2_saved_distrib
  test_budget_points_w_CO2_distrib: test_budget_points_w_CO2_distrib
  mode_scale_colors: mode_scale_colors
  mode_scale_fill: mode_scale_fill
  in_preset_Car_Trips_Daily_Avg: in_preset_Car_Trips_Daily_Avg
  flag_preset_Car_Trips_Daily_Avg: flag_preset_Car_Trips_Daily_Avg
  in_preset_elec_gen_emissions: in_preset_elec_gen_emissions
  flag_preset_elec_gen_emissions: flag_preset_elec_gen_emissions
  in_preset_ICE_Fuel_Economy: in_preset_ICE_Fuel_Economy
  flag_in_preset_ICE_Fuel_Economy: flag_in_preset_ICE_Fuel_Economy
  in_preset_EBike: in_preset_EBike
  in_preset_EBike_2: in_preset_EBike_2
  flag_in_preset_EBike: flag_in_preset_EBike
  in_preset_BEV: in_preset_BEV
  flag_in_preset_BEV: flag_in_preset_BEV
  in_preset_PHEV: in_preset_PHEV
  flag_in_preset_PHEV: flag_in_preset_PHEV
  in_preset_FCEV: in_preset_FCEV
  flag_in_preset_FCEV: flag_in_preset_FCEV
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Get packages
library(knitr)
library(scales)
library(kableExtra)
library(htmltools)

#Define millions formatting function
print.million <- function(x, quote = FALSE) {
  x <- paste0(round(x / 1e6, 1), "M")
}

```

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri("logo.png"), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;',
               height = '100px')
```

## Introduction

The E-Vehicle Incentive Impact Tool allows users to better understand the cost, carbon emissions reduction, and carbon emissions reduction cost efficiency given a specific e-vehicle incentive program and local emissions profiles. 

## Results
```{r costperkg, echo=FALSE}
#Cost per kg CO2 saved by mode
print(g1plot(params$costperkg, params$test_points, params$costperkg_x, params$costperkg_y, params$mode_scale_colors))

#update table such that its values are formatted correctly
test_points <- params$test_points %>% 
  mutate(mode = recode(mode, `EBike` = "E-Bike")) %>% 
  mutate(incentive = paste("$", format(round(incentive, 2L), nsmall = 2L))) %>% 
  mutate(costperkg = paste("$", format(round(costperkg, 2L), nsmall = 2L))) %>% 
  mutate(CO2_saved = paste(format(round(CO2_saved, 2L)), "kg")) %>% 
  select(mode, incentive, CO2_saved, costperkg) #reorder the columns

#Table, Cost per kg CO2 saved by mode
kable(test_points,
      digits = 2,
      col.names = c("Mode", "Incentive Amount", "CO2 saved per vehicle, per year", "Cost per kg CO2 Saved"),
      align = rep('l', ncol(test_points)))  %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

The Cost per kg CO2 saved results show the dollar amount per kg of CO2 that was avoided thanks to the incentive program. It is calculated by subtracting emissions of the e-vehicle from the average ICE vehicle using the given average travel day behavior. In the case of e-bikes, the total CO2 remissions is the sum of the miles replaced by e-bike and the remaining unreplaced miles traveled by ICE automobile. In this case, the test points assume that the entire budget is spent on that e-vehicle type. This is done in order to demonstrate the cost efficiency of each e-vehicle type.

For this plot, **lower is better**.

``` {r num_incentivized, echo=FALSE}
#Number incentivized
print(g2plot(params$num_incentivized, params$test_budget_points, params$num_x, params$num_y, params$mode_scale_colors))

#update table such that its values are formatted correctly
test_budget_points <- params$test_budget_points %>% 
  mutate(mode = recode(mode, `EBike` = "E-Bike"),
         budget = paste("$", format(print.million(budget), nsmall = 2L)),
         num = floor(num))

#Table, Number incentivized
kable(test_budget_points,
      col.names = c("Mode", "Total Budget", "Number of Incentives"),
      align = rep('l', ncol(test_budget_points))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

The number of vehicles incentivized results show the number of vehicles that the total budget is able to accomodate, assuming only one type of e-vehicle is incentivized at a time.

For this plot, **higher is better**.

``` {r CO2_saved, echo=FALSE}
#CO2 saved
print(g3plot(params$CO2_saved, params$test_budget_points_w_CO2, params$num_incentivized, params$CO2_saved_x, params$CO2_saved_y, params$mode_scale_colors))

#Update table such that its values are formatted correctly
test_budget_points_w_CO2 <- params$test_budget_points_w_CO2 %>% 
  mutate(mode = recode(mode, `EBike` = "E-Bike"),
         budget = paste("$", format(print.million(budget), nsmall = 2L)),
         total_CO2_saved = paste(format(print.million(total_CO2_saved), nsmall = 2L), "kg")) %>% 
  select(mode, budget, total_CO2_saved)

#Table, CO2 saved
kable(test_budget_points_w_CO2,
      col.names = c("Mode", "Total Budget", "Total CO2 Saved, per year"),
      align = rep('l', ncol(test_budget_points_w_CO2))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

The CO2 saved results demonstrate the potential total kg CO2 saved given a specific budget and incentive amount. This assumes only one type of e-vehicle is incentivized at a time.

For this plot, **higher is better**.

``` {r num_incentivized_distrib, echo=FALSE}
#Budget distribution specific number incentivized
print(g4plot(params$num_incentivized, params$num_incentivized_distrib, params$test_budget_points_distrib, params$num_x, params$num_y, params$mode_scale_colors, params$mode_scale_fill))

#Update table such that its values are formatted correctly
test_budget_points_distrib <- params$test_budget_points_distrib %>% 
  mutate(mode = recode(mode, `EBike` = "E-Bike"),
         budget = paste("$", format(print.million(budget), nsmall = 2L)),
         budget_portion_perct = percent(budget_portion_perct),
         budget_portion = paste("$", format(print.million(budget_portion), nsmall = 2L)),
         num = floor(num))

#Table, Budget distribution specific number incentivized
kable(test_budget_points_distrib,
      col.names = c("Mode", "Total Budget", "Allotted Percent of Total Budget", "Allotted Portion of Total Budget", "Number of Incentives"),
      align = rep('l', ncol(test_budget_points_distrib))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

The number incentivized, budget distribution specific results show the total number of e-vehicles and total number of e-vehicles by type that can be incentivized given a specific budget and the portion of that budget alloted to each e-vehicle type.

For this plot, **higher is better**.

``` {r CO2_saved_distrib, echo=FALSE}
#Budget distribution specific CO2 saved
print(g5plot(params$num_incentivized, params$CO2_saved_distrib, params$test_budget_points_w_CO2_distrib, params$CO2_saved_x, params$CO2_saved_y, params$mode_scale_colors, params$mode_scale_fill))

#Update table such that its values are formatted correctly
test_budget_points_w_CO2_distrib <- params$test_budget_points_w_CO2_distrib %>% 
  mutate(mode = recode(mode, `EBike` = "E-Bike"),
         budget = paste("$", format(print.million(budget), nsmall = 2L)),
         total_CO2_saved = paste(format(print.million(total_CO2_saved), nsmall = 2L), "kg")) %>% 
  select(mode, budget, total_CO2_saved)

#Table, Budget distribution specific CO2 saved
kable(test_budget_points_w_CO2_distrib,
      col.names = c("Mode", "Total Budget", "Total CO2 Saved by this mode"),
      align = rep('l', ncol(test_budget_points_w_CO2_distrib))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

The CO2 saved, budget distribution specific results show the total kg CO2 saved and and total kg CO2 saved by type given a specific budget and the portion of that budget alloted to each e-vehicle type.

For this plot, **higher is better**.

## Inputs

In this section, the inputs that were provided to the tool are displayed.
```{r trips, echo = FALSE}
#Pre allocate the table
N = 2
trips <- data.frame(Name = rep("", N), Value = rep(NA, N), Unit = rep("", N), Preset = rep("", N), stringsAsFactors = F)

#Learn if a preset was used or not
if (params$flag_preset_Car_Trips_Daily_Avg) {
  trips_preset = params$in_preset_Car_Trips_Daily_Avg
} else {trips_preset = "User Defined"}

#Build the table
trips[1,] <- list("Average Trips per Day", params$Car_Trips_Daily_Avg, "Trips", trips_preset)
trips[2,] <- list("Average Auto Trip Length", params$Car_Trip_Avg_Length, "mi", trips_preset)

#Display the table
kable(trips, caption = "Trips",
      align = rep('l', ncol(trips))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

The trips table shows the average number of automobile trips per household per day and the average number of automobile trip length in the region. Typically these values are obtained using from household travel surveys.

```{r electricity, echo = FALSE}
#Pre allocate the table
N = 1
elec <- data.frame(Name = rep("", N), Value = rep(NA, N), Unit = rep("", N), Preset = rep("", N), stringsAsFactors = F)

#Learn if a preset was used or not
if (params$flag_preset_elec_gen_emissions) {
  elec_preset = params$in_preset_elec_gen_emissions
} else {elec_preset = "User Defined"}

#Build the table
elec[1,] <- list("Electricity Carbon Emissions", params$elec_gen_emissions, "lb CO2 / MWh", elec_preset)

#Display the table
kable(elec, caption = "Electricity",
      align = rep('l', ncol(elec))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

The electricity table shows the average carbon intensity of electricity generation in the given region. This information can be obtained from the [US EPA's eGRID](https://www.epa.gov/energy/emissions-generation-resource-integrated-database-egrid).

```{r ICE, echo = FALSE}
#Pre allocate the table
N = 2
ICE <- data.frame(Name = rep("", N), Value = rep(NA, N), Unit = rep("", N), Preset = rep("", N), stringsAsFactors = F)

#Learn if a preset was used or not
if (params$flag_in_preset_ICE_Fuel_Economy) {
  ICE_preset = params$in_preset_ICE_Fuel_Economy
} else {ICE_preset = "User Defined"}

#Build the table
ICE[1,] <- list("Average Fuel Economy", params$ICE_Fuel_Economy, "mpg", ICE_preset)
ICE[2,] <- list("Carbon Emissions from Gasoline", drop_units(set_units(set_units(1, "gal"), CO2_g)), "g CO2/gal", "(Constant)")

#Display the table
kable(ICE, caption = "ICE",
      align = rep('l', ncol(ICE))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

The ICE (internal combustion engine) table shows the average fuel economy of an automobile. The carbon emissions from gasoline was obtained from the [US EPA](https://www.epa.gov/energy/greenhouse-gases-equivalencies-calculator-calculations-and-references).

```{r EBike, echo = FALSE}
if (params$EBike_include) { #only include if "include" tickbox checked in GUI
  #Pre allocate the table
  N = 2
  EBike <- data.frame(Name = rep("", N), Value = rep(NA, N), Unit = rep("", N), Preset = rep("", N), stringsAsFactors = F)
  
  #Learn if a preset was used or not
  if (params$flag_in_preset_EBike) {
    EBike_preset = params$in_preset_EBike
    EBike_preset_2 = paste(params$in_preset_EBike_2, "Efficiency")
  } else {
    EBike_preset = "User Defined"
    EBike_preset_2 = NULL
  }
  
  #Build the table
  EBike[1,] <- list("Average Economy", params$EBike_econ, "kWh/100 mi", paste(EBike_preset, EBike_preset_2))
  EBike[2,] <- list("Ratio, portion of car miles replaced by e-bike (maximum 1)", params$EBike_VMT_r, "", "User Defined")
  
  #Display the table
  kable(EBike, caption = "E-Bike",
      align = rep('l', ncol(EBike))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}

```

`r if (params$EBike_include) {"The E-Bike table shows the average fuel economy of e-bikes eligible for an e-bike incentive.This value can be obtained from e-bike manufacturers. Data used for presets was obtained from a report published by [Efficiency Vermont](https://www.efficiencyvermont.com/Media/Default/docs/white-papers/efficiency-vermont-electric-bike-white-paper.pdf) Additionally, the ratio of automobile miles that are replaced by e-bike miles is specified. This value can be obtained from local e-bike use studies."}`

``` {r BEV, echo = FALSE}
if (params$BEV_include) { #only include if "include" tickbox checked in GUI
  #Pre allocate the table
  N = 1
  BEV <- data.frame(Name = rep("", N), Value = rep(NA, N), Unit = rep("", N), Preset = rep("", N), stringsAsFactors = F)
  
  #Learn if a preset was used or not
  if (params$flag_in_preset_BEV) {
    BEV_preset = params$in_preset_BEV
  } else {BEV_preset = "User Defined"}
  
  #Build the table
  BEV[1,] <- list("Average Fuel Economy", params$BEV_econ, "kWh / 100 mi", BEV_preset)
  
  #Display the table
  kable(BEV, caption = "BEV",
      align = rep('l', ncol(BEV))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}

```

`r if (params$BEV_include) {"The BEV (Battery Electric Vehicle) table shows the average fuel economy of BEVs eligible for an incentive. This value can be obtained from the fuel economy information provided by the [US EPA](https://www.fueleconomy.gov/)."}`

``` {r PHEV, echo = FALSE}
if (params$PHEV_include) { #only include if "include" tickbox checked in GUI
  #Pre allocate the table
  N = 3
  PHEV <- data.frame(Name = rep("", N), Value = rep(NA, N), Unit = rep("", N), Preset = rep("", N), stringsAsFactors = F)
  
  #Learn if a preset was used or not
  if (params$flag_in_preset_PHEV) {
    PHEV_preset = params$in_preset_PHEV
  } else {PHEV_preset = "User Defined"}
  
  #Build the table
  PHEV[1,] <- list("Average E-Mode Fuel Economy", params$PHEV_elec_econ, "kWh / 100 mi", PHEV_preset)
  PHEV[2,] <- list("Average E-Mode Range", params$PHEV_range_elec, "mi", PHEV_preset)
  PHEV[3,] <- list("Average ICE Mode Fuel Economy", params$PHEV_ICE_econ, "mpg", PHEV_preset)
  
  #Display the table
  kable(PHEV, caption = "PHEV",
      align = rep('l', ncol(PHEV))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}

```

`r if (params$PHEV_include) {"The PHEV (Plug-in Hybrid Electric Vehicle) table shows the average fuel economies of PHEVs eligible for an incentive. The Average E-Mode Fuel Economy is used for the E-Mode range of the daily average miles traveled. Thereafter, the ICE Mode Fuel Economy is used. The sum of emissions from both types of propulsion are used to calculate total emissions."}`

``` {r FCEV, echo = FALSE}
if (params$FCEV_include) { #only include if "include" tickbox checked in GUI
  #Pre allocate the table
  N = 3
  FCEV <- data.frame(Name = rep("", N), Value = rep(NA, N), Unit = rep("", N), Preset = rep("", N), stringsAsFactors = F)
  
  #Learn if a preset was used or not
  if (params$flag_in_preset_FCEV) {
    FCEV_preset = params$in_preset_FCEV
  } else {FCEV_preset = "User Defined"}
  
  #Build the table
  FCEV[1,] <- list("Average Fuel Economy", params$FCEV_econ, "mi / kg H2", FCEV_preset)
  FCEV[2,] <- list("Ratio, Amount of electricity for electrolysis produced by 100% renewable sources (maximum 1)", params$renew_energy_ratio, "", "User Defined")
  FCEV[3,] <- list("Electricity required to electrolyze 1 kg H2", drop_units(set_units(set_units(1, "H2_kg"), kiloWatthour)), "kWh", "(Constant)")
  
  #Display the table
  kable(FCEV, caption = "FCEV",
      align = rep('l', ncol(FCEV))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
}
```

`r if (params$FCEV_include) {"The FCEV (Fuel Cell Electric Vehicle) table shows the average fuel economy of FCEVs eligible for an incentive. Additionally, it shows the ratio of electricity used for electrolysis that is provided by 100% renewable sources. Lastly, it specifies the electricity required to electrolyze H2, provided by [energy.gov](https://www.energy.gov/eere/fuelcells/doe-technical-targets-hydrogen-production-electrolysis)."}`

```{r Incentives, echo = FALSE}
#Pre allocate the table
N = 5
incentives_input <- data.frame(mode = rep("", N), Name = rep("", N), Value = rep(NA, N), stringsAsFactors = F)

#Build the table
incentives_input[1,] <- list("","Total E-Vehicle Budget", paste("$", format(print.million(params$test_budget), nsmall = 2L)))
incentives_input[2,] <- list("EBike","E-Bike Incentive", paste("$", params$EBike_incentive))
incentives_input[3,] <- list("BEV","BEV Incentive", paste("$", params$BEV_incentive))
incentives_input[4,] <- list("PHEV","PHEV Incentive", paste("$", params$PHEV_incentive))
incentives_input[5,] <- list("FCEV","FCEV Incentive", paste("$", params$FCEV_incentive))

#Remove unecessary rows
incentives_input <- exclude_items(incentives_input, params$EBike_include, params$PHEV_include, params$BEV_include, params$FCEV_include) %>% 
  select(-mode)

#Display the table
kable(incentives_input,
      caption = "Total Budget and Incentive Amounts",
      align = rep('l', ncol(incentives_input))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

The Incentives table shows the total E-Vehicle incentive budget and the incentive provided to the consumer by e-vehicle type.

``` {r Incentives Distribution, echo = FALSE}

#Clean up the table
inputs_num_incentivized_distrib <- params$num_incentivized_distrib %>% 
  select(mode, in_per_budget) %>% #select just relevant columns
  distinct(mode, .keep_all = T) %>%  #Filter for just one row of each mode
  mutate(mode = recode(mode, `EBike` = "E-Bike"),
         in_per_budget = percent(in_per_budget))
  

#Display the table
kable(inputs_num_incentivized_distrib,
      col.names = c("Mode", "Allotted Percent of Total Budget"),
      caption = "Budget Distribution",
      align = rep('l', ncol(inputs_num_incentivized_distrib))) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

The budget distribution table shows what percent of the total budget is allotted for which types of e-vehicle.